Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/20-related-work.tex
OCR XP protocol
Updates from Overleaf

Most of the current state-of-the-art open-source OCR systems, like Tesseract \cite{smith2007overview}, OCRopus \cite{breuel2008ocropus}, and the recent Kraken~\cite{kraken}, Calamari~\cite{wick_calamari_2020} and \peroocr \cite{kohut2021ts} are based on a pipeline of convolutional neural networks (CNNs) and long short-term memory networks (LSTM).
Although this kind of model produces good results with modern texts, it faces several challenges with ancient texts, such as the lack of annotated data for learning, or different transcription styles in training data.
%
% \cite{martinek2019hybrid} propose an approach to generate synthetic annotated text for historical OCR training, based on manually collected characters from historical text images.
% This work proposes to train an OCR system based on a CNN-LSTM network with synthetic data and then to fine-tune the model with some pages of real historical annotated text.
% The results show that this approach gives state-of-the-art results.

@@

\subsection{Pipeline summary}

>>>>

Most of the current state-of-the-art open-source OCR systems, like Tesseract \cite{smith2007overview}, OCRopus \cite{breuel2008ocropus}, and the recent Kraken~\cite{kraken}, Calamari~\cite{wick_calamari_2020} and \peroocr \cite{kohut2021ts} are based on a pipeline of convolutional neural networks (CNNs) and long short-term memory networks (LSTM).
Although this model produces good results with modern texts, it still faces challenges with ancient texts, such as the lack of annotated data for learning, or different transcription styles for training data.
%
% \cite{martinek2019hybrid} propose an approach to generate synthetic annotated text for historical OCR training, based on manually collected characters from historical text images.
% This work proposes to train an OCR system based on a CNN-LSTM network with synthetic data and then to fine-tune the model with some pages of real historical annotated text.
% The results show that this approach gives state-of-the-art results.

@@

\subsection{Pipeline summary}
\label{sec:pipeline-summary}

### 2022-01-20 src-latex/parts/30-dataset.tex
Updates from Overleaf

These pieces of information constituting the structure of the entries are the basic data that we want to extract, deduplicate, and structure to build a spatio-temporal database of XIX\textsuperscript{th} century Parisian inhabitants and businesses. Except for some potentially wordy activity descriptions, they correspond to named entities. However, while most entries contain the same types of named entities, their order and the way they are written vary from one directory or index to another. To provide examples of each entry structure, pages from each type have thus been annotated. %\footnote{In this work, the street name index entries have not been included as they are very different from the others. The strategy to be adopted to process them without loss of quality for the NER model will be the subject of future work.}.

@@

The evaluation metrics are illustrated on~\cref{fig.eval-ocr-ner}. The OCR text and the groundtruth are first aligned to
evaluate the OCR accuracy. As there are 11 mismatches over 56 aligned characters, the CER is thus 24\%. This alignment
is then used to back-project the groundtruth tags to build the tagged NER-\emph{target}. Finally, the NER system runs on the
OCR text; its output is compared to the NER groundtruth. There is only 2 over 3 tags matching in the prediction (precision),
while only 2 over 4 entities are matched in the reference (recall). It follows an overall f-score of 0.4.

>>>>

These pieces of information stored in the entries are the basic data that we want to extract, deduplicate, and structure to build a spatio-temporal database of XIX\textsuperscript{th} century Parisian inhabitants and businesses. Except for some potentially wordy activity descriptions, they correspond to named entities. However, while most entries contain the same types of named entities, their order and the way they are written vary from one directory/index to another. To provide examples of each entry structure, pages from each type have thus been annotated. %\footnote{In this work, the street name index entries have not been included as they are very different from the others. The strategy to be adopted to process them without loss of quality for the NER model will be the subject of future work.}.

@@

The evaluation metrics are illustrated on~\cref{fig.eval-ocr-ner}. The OCR text and the groundtruth are first aligned to
evaluate the OCR accuracy. As there are 11 mismatches over 56 aligned characters, the CER is thus 24\%. This alignment
is then used to back-project the groundtruth tags to build the tagged NER-\emph{target}. Finally, the NER system runs on the
OCR text; its output is compared to the NER groundtruth. There is only 2 over 3 tags matching in the prediction (precision),
while only 2 over 4 entities are matched in the reference (recall). It follows an overall F1-score of 0.4.

### 2022-01-20 src-latex/parts/80-conclusion.tex
Updates from Overleaf

% !TeX root = ../main-paper.tex
\section{Conclusion}

In this article, we assessed the performance of three modern OCR systems on real historical data. Although Pero-OCR clearly outperforms its competitors, the qualitative analysis of its errors shows that it fails on different entries. This calls for leveraging both Pero-OCR and Tesseract in a complementary way to get the best out of both systems. Moreover, we evaluated the needs of two deep-learning-based NER approaches in terms of training data amount and text quality for pretraining. We showed that BERT-based NER can benefit from pretraining and fine-tuning on a noisy OCR corpus to improve its performance on a noisy OCRed test dataset. To perform a NER task on OCR texts, it seems therefore worthwhile to train the NER model on a corpus OCRed with the same system and not corrected. However, the results are not as good as for clean text: it is therefore interesting to investigate how to improve the OCR results or to correct the text in a postprocessing step. Furthermore, it seems that the models quickly achieve good performance with very few training examples. Leveraging a model fine-tuned on a few examples to automatically produce much larger training sets could reveal a solution to lower the annotation burden. Besides, as directory entries always have the same structure - at least within a given index - we could take advantage of NER results and some simple rules to identify entries within pages instead of relying on the page layout.
%Interesting points to discuss:
%\begin{itemize}
%    \item can we train on noisy data? (without manual OCR correction?) => future work? cf Pero OCR training procedure?
%    \item do we need better OCR systems or better post-correction techniques (if NER is reliable enough)?
%    \item Construction of the lexicon and associated cost \nathalie{là je ne comprends pas}
%\end{itemize}
%Ideas for future work:
%\begin{itemize}
%    \item Evaluate this: fine-tune Spacy NER on a few samples to generated a bootstrap dataset, feed it to BERT (cleaned or raw) to create an good model with minimal efforts ? \nathalie{les résultats de la table 2 ne plaident pas vraiment pour ça: même sur les très petits corpus, spacy est tours derrière...}
%    \item Use ML to infer regexes ?
%    \item As directories entries are always structured the same way (in a given list at least): use NER to identify entries within pages to save the burden of having to rely on the page layout ?
%\end{itemize}

>>>>

% !TeX root = ../main-paper.tex
\section{Conclusion}
We assessed the performance of three modern OCR systems on real historical data.
Although Pero-OCR clearly outperforms its competitors, the qualitative analysis of OCR errors shows that the failure cases are not the same for Pero and Tesseract.
This calls for leveraging both OCR systems in a complementary way to get the best of the two worlds.
%Moreover, we evaluate two deep-learning-based NER approaches in terms of their sensibility to the amount of training data and to noisy OCR texts.
The evaluation of SpaCy NER and CamemBERT (with and without pre-training) showed that BERT-based NER can benefit from pre-training and fine-tuning on a corpus produced with the same process than the texts to annotate.
%However, the results are not as good as for clean text: it is therefore interesting to investigate how to improve the OCR results or to correct the text in a postprocessing step.
Furthermore, it seems that all three models achieve good performance with relatively few training examples.
With a F1-score of 92\% with only 49 training examples, the pre-trained CamemBERT model seems to be a good choice to serve as a bootstrapping model in order to quickly produce large training sets and therefore lower the burden of creating a ground truth from scratch.
Besides, as directory entries always have the same structure - at least within a given index - we could take advantage of NER results and some simple rules to identify entries within pages instead of relying on the page layout.
%Interesting points to discuss:
%\begin{itemize}
%    \item can we train on noisy data? (without manual OCR correction?) => future work? cf Pero OCR training procedure?
%    \item do we need better OCR systems or better post-correction techniques (if NER is reliable enough)?
%    \item Construction of the lexicon and associated cost \nathalie{là je ne comprends pas}
%\end{itemize}
%Ideas for future work:
%\begin{itemize}
%    \item Evaluate this: fine-tune Spacy NER on a few samples to generated a bootstrap dataset, feed it to BERT (cleaned or raw) to create an good model with minimal efforts ? \nathalie{les résultats de la table 2 ne plaident pas vraiment pour ça: même sur les très petits corpus, spacy est tours derrière...}
%    \item Use ML to infer regexes ?
%    \item As directories entries are always structured the same way (in a given list at least): use NER to identify entries within pages to save the burden of having to rely on the page layout ?
%\end{itemize}
